Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2018-10-09 reports/preprint.tex
Typo
Edit

%
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/head_groups}
\caption{\label{fig:heads}\small The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
\end{figure}
%
We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of reflectometry measurements at different surface concentration.
The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by XRR at a series of different surface pressures, between \SIrange{15}{40}{\milli\newton\per\meter}.
Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
Instead these parameters, along with the thickness of the phospholipid head layer, $d_h$, were allowed to vary for each lipid.
However, their values were constained to be self-consistent for a single lipid over multiple measurements at different surface pressures.

@@

In keeping with this previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
In all cases the surface roughness was found to be higher than in water. However this should be considered in the context that the absolute surface tension of the DES is less than water with a corresponding higher surface roughness\cite{Arnold2015}.

>>>>

%
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{figures/head_groups}
\caption{\label{fig:heads}\small The two lipid classes with different head groups compared in this study, where R indicates the hydrocarbon tail; (a) phosphatidylglycerol (PG), (b) phosphocholine (PC).}
\end{figure}
%
We developed a chemically-consistent model (detail in the ESI) that allowed for the co-refinement of reflectometry measurements at different surface concentration.
The model was applied to the study of four phospholipids monolayers, namely 1,2-dipalmitoyl-sn-glycero-3-phosphocholine (DPPC, C$_{16}$ tails), 1,2-dimyristoyl-sn-glycero-3-phosphocholine (DMPC, C$_{14}$ tails),  1,2-dilauroyl-sn-glycero-3-phosphocholine (DLPC, C$_{12}$ tails) and 1,2-dimyristoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (DMPG, C$_{14}$ tails), at the air-1:2 choline choride:glycerol mixture interface, by XRR at a series of different surface pressures, between \SIrange{15}{40}{\milli\newton\per\meter}.
Unlike monolayer models applied previously\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990}, our model made no assumption of the volume of the lipid head, $V_h$, or tail, $V_t$.
Instead these parameters, along with the thickness of the phospholipid head layer, $d_h$, were allowed to vary for each lipid.
However, their values were constrained to be self-consistent for a single lipid over multiple measurements at different surface pressures.

@@

In keeping with previous literature, \cite{Mohwald1990,Vaknin1991}, the tail layer thickness, $d_t$, increases with the number of hydrocarbon atoms present.
Furthermore, the thickness of the tail layers agrees well with values found for water-analogues; \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water for DMPC, and \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water for DPPC.
In all cases the surface roughness was found to be higher than in water. However this should be considered in the context that the absolute surface tension of the DES is less than water with a corresponding higher surface roughness\cite{Arnold2015}.
